---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# squeal

<!-- badges: start -->
[![R-CMD-check](https://github.com/asenetcky-r-pkgs/squeal/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/asenetcky-r-pkgs/squeal/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`squeal` makes working with the SQL servers a breeze. There are basic functions
for the most common tasks easier and faster to program and safer to 
execute. `squeal` is primarily meant to serve as a template for internal/private
packages where it is a base to layer wrapper functions with pre-filled
arguments for ease of use and standardizing SQL einteractions across a team.

## Installation

You can install the development version of sql like so:

``` {r install}
# remotes::install(
# https://github.com/asenetcky-r-pkgs/squeal.git
# git = "external")
```

```{r setup}
library(squeal)
```


## Basics

`squeal` has the basics but with checks built in to ensure developers
can be as safe as reasonably expected.

```{r basics, eval=FALSE}

conn <- dbplyr::simulate_mssql()
database <- "fake_database"
schema <- "fake_schema"
table <- "fake_table"

important_data <-
  dplyr::tibble(
    col1 = 1:10,
    col2 = 1:10,
    col3 = 1:10
  )

# Survey a table
# Grab basic information about the table from the comfort of your IDE
survey_table(
  conn,
  database,
  schema,
  table
)

# Create a table
create_table(
  important_data,
  conn,
  database,
  schema,
  table
)


# Read a table
read_table(
  conn,
  database,
  schema,
  table,
  lazy = FALSE # set TRUE for lazily-evaluated tables!
)

# Append to a table
append_table(
  important_data,
  conn,
  database,
  schema,
  table
)

# Truncate a table
truncate_table(
  conn,
  database,
  schema,
  table
)

# Drop a table
nuke_table(
  conn,
  database,
  schema,
  table
)
```
